Torontonians Prefer to Get Married in the Warmer Half of the Year

### 2024-01-24 outputs/paper/paper.qmd
updated comments
updates writing

---
title: "Torontonians Prefer to Get Married in the Warmer Half of the Year"
author: Diana Liu
thanks: "Code and data are available at: https://github.com/Diana-Guanzhi-Liu/Analysis-of-Toronto-Marriages"
date: 25 January 2024
abstract: "We examine marriage licenses obtained in the city of Toronto in the year 2022 and 2023 by months, dividing the year into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, Febuary, March). We found that the number of marriage licenses obtained in 2022 increased by 117% between cold and warm months and 68% in 2023. This supports our hypothesis that Torontonians prefer to get married during the warmer half of the year."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Introduction
According to @citebusinessinsider, summer is the hottest time to get married due to more dress options, the opportunity to have an outdoor wedding, and relatively easier travel among other reasons, but is this actually true in Toronto? Toronto is a city known for cold weather in the winter with snow from October to March (@citeurbanclimate). This means that we expect the amount of marriage licenses obtained in Toronto should increase during the warm months of April through September and decrease during the cold months of October through March. By knowing whether or not more marriages occur during the summer months, prospective couples in Toronto can plan ahead and avoid peak seasons for applying for a marriage license and any delays that result.

In the Data section, we download marriage license data from opendatatoronto(@citeopendata), a database maintained by the City of Toronto. This dataset features the number of marriage licenses issued in Toronto by month, beginning January 1 2011. We will be looking at data from 2023 and 2022, as well as any changes in the number of marriage licenses between the two years.

We formulate our hypothesis to be that there are more marriage licenses obtained in warm months of April to September than cold months of October to March because Torontonians prefer to get married during the warmer half of the year. We analyzed the data in the Results section by plotting the number of licenses against the month in which they were obtained so we can see the change in the number of marriage licenses from month to month. Since there are only 12 data points in each graph, we are also able to label each observation with the exact number of marriage licenses issued. Then we calculated the total amount and the average amount of marriage licenses in the warm months and cold months of each year, and the percent change between them. Our results show that our hypothesis is correct with the number of marriage licenses steadily increasing from February to May, peaking around July, then decreasing between September and November before hitting its lowest in January. This cyclic nature can be observed for both 2022 and 2023.

*insert discussion in intro

@@

## Weaknesses and Next Steps
A weakness in our analysis is the small quantity of data that was used to come to our conclusion. While the pattern of increased marriage licenses was present in both 2022 and 2023, this might not have been the case in prior years. Performing the same analysis on years 2011 to 2021 will confirm our results.

>>>>

---
title: "Torontonians Prefer to Get Married in the Warmer Half of the Year"
author: Diana Liu
thanks: "Code and data are available at: https://github.com/Diana-Guanzhi-Liu/Analysis-of-Toronto-Marriages"
date: 25 January 2024
abstract: "I examine marriage licenses obtained in the city of Toronto in the year 2022 and 2023 by months, dividing the year into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, Febuary, March). I found that the number of marriage licenses obtained in 2022 increased by 117% between cold and warm months and 68% in 2023. This supports the hypothesis that Torontonians prefer to get married during the warmer half of the year."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Introduction
According to @citebusinessinsider, summer is the hottest time to get married in the United States, but I want to know if this is true in Toronto as well. Toronto is a city known for cold weather in the winter with snow from October to March (@citeurbanclimate), so it makes sense for Torontonians to prefer the warmer months of April to September. This means that we expect the amount of marriage licenses obtained in Toronto should be higher during the warm months of April through September than the cold months of October through March. By knowing whether or not more marriages occur during the summer months, prospective couples in Toronto can plan ahead and avoid peak seasons for applying for a marriage license and any delays that result.

In the Data section, I download marriage license data from opendatatoronto(@citeopendata), a database maintained by the City of Toronto. This data set features the number of marriage licenses issued in Toronto by month, beginning January 1 2011. I will only be looking at data from 2023 and 2022, this is because some data is missing in 2021, and covid-19 lock downs means that 2020 data is inaccurate.

I formulated my hypothesis to be that there are more marriage licenses obtained in warm months of April to September than cold months of October to March because Torontonians prefer to get married during the warmer half of the year. I analyzed the data in the Results section by plotting the number of licenses against the month in which they were obtained so we can see the change in the number of marriage licenses from month to month. Since there are only 12 data points in each graph, I labeled each observation with the exact number of marriage licenses issued. Then I calculated the total amount and the average amount of marriage licenses in the warm months and cold months of each year, and the percent change between them. My results show that the hypothesis is correct with the number of marriage licenses steadily increasing from February to May, peaking around July, then decreasing between September and November before hitting its lowest in January.

The cyclical appearance of the number of marriage licenses in both 2023 and 2023...

@@

## Weaknesses and Next Steps
A weakness in my analysis is the small quantity of data that was used to come to our conclusion. While the pattern of increased marriage licenses was present in both 2022 and 2023, this might not have been the case in prior years. Performing the same analysis on years 2011 to 2021 will confirm our results.
